---
title: "rpgcolorsr User Guide"
author: "Brian Froeb"
date: "6/29/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r echo=FALSE}
library(ggplot2)
library(tmap)
library(rpgcolorsr)
data(NLD_muni)
```

There are currently 71 colors included in this package the color names and their hex codes are below
```{r, echo=FALSE}
rpg_color_list
```

These are grouped into 20 color palettes, the colors included in each palette and their hex codes are below
```{r, echo=FALSE}
rpg_color_palettes
```

These color palettes can be inserted into ggplot graphics, examples of each palettes in ggplot are below

## Functions Included

This package includes four functions:

-rpg_cols()
-rpg_color_pal()
-scale_color_rpg()
-scale_fill_rpg()

#### rpg_cols
takes a input string or group of strings and returns the hex code. 
The color must be one of the colors included in this package

##### Example:
```{r}
rpg_cols("blue")

rpg_cols("teal", "black")
```

#### rpg_color_pal

Converts an input string representing a color palette into a function that can be converted into a usable color palette.

```{r}
rpg_color_pal("rpg_cold_warm")
```

By adding a step count after the function it will return a usable palette

```{r}
rpg_color_pal("rpg_cold_warm")(10)
```

These palettes can be reversed as needed

```{r}
rpg_color_pal("rpg_cold_warm", reverse = TRUE)(10)
```

#### scale_color_rpg and scale_fill_rpg

These functions supply a fill or color to a ggplot call. See examples below.

## Scale Color Examples

### Discrete Palettes
```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "logo")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "additional")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "main and additional")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "rpg_colors")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "rpg_cold_warm")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "rpg_rainbow")
```

### Discrete Palettes
```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "shale_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "green_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "red_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "earth_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "teal_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_orange_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "sea_green_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_blue_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "black_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "chartreuse_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "gold_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "burnt_orange_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_colors")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_cold_warm")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_rainbow")
```


## Scale Fill Examples
```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "logo", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "additional", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "main and additional", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "shale_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "green_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "red_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "earth_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "teal_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_orange_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "gray_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "sea_green_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_blue_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "navy_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "black_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "chartreuse_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "gold_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "burnt_orange_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_colors", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_cold_warm", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_rainbow", guide = "none")
```


## Geographic Data with ggplot2

These palettes can also be used with ggplot2 to display geographic data with both continuous and discrete scales, uses the scale fill function.

### Discrete Palettes
```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "logo")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "additional")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "main and additional")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "rpg_colors")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "rpg_cold_warm")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "rpg_rainbow")
```

### Continous Palettes
```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "logo", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "additional", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "main and additional", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "shale_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "green_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "red_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "earth_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "teal_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_orange_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "gray_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "sea_green_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_blue_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "navy_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "black_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "chartreuse_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "gold_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "burnt_orange_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_colors", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_cold_warm", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_rainbow", discrete = FALSE)
```

## Geographic Data with tmap

tmap uses a differing syntax from ggplot however by using the rpg_color_pal function, with a step count indicated, and saving the output to an object these palettes can be used in tmap.

### Discrete Palettes
```{r}
MyPal <- rpg_color_pal("logo")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("main and additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_colors")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_cold_warm")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_rainbow")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

### Continous Palettes
```{r}
MyPal <- rpg_color_pal("logo")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("main and additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("shale_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("green_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("red_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("earth_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("teal_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_orange_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("gray_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("sea_green_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_blue_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("navy_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("black_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("chartreuse_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("gold_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("burnt_orange_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_colors")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_cold_warm")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_rainbow")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```
