---
title: "rpgcolorsr Examples"
author: "Brian Froeb"
date: "6/29/2020"
output: html_document
---
```{r echo=FALSE}
library(ggplot2)
library(tmap)
library(rpgcolorsr)
data(NLD_muni)
```
# Exmaples {.tabset}

## Scale Color Examples

### Discrete Palettes
```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "logo")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "additional")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "main and additional")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "rpg_colors")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "rpg_cold_warm")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_rpg(palette = "rpg_rainbow")
```

### Discrete Palettes
```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "shale_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "green_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "red_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "earth_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "teal_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_orange_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "sea_green_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_blue_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "black_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "chartreuse_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "gold_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "burnt_orange_ramp")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_colors")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_cold_warm")
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Sepal.Length)) +
  geom_point(size = 4) +
  scale_color_rpg(discrete = FALSE, palette = "rpg_rainbow")
```


## Scale Fill Examples

### Discrete Palettes
```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "logo", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "additional", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "main and additional", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "shale_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "green_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "red_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "earth_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "teal_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_orange_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "gray_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "sea_green_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_blue_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "navy_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "black_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "chartreuse_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "gold_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "burnt_orange_ramp", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_colors", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_cold_warm", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_rainbow", guide = "none")
```

```{r}
ggplot(mpg, aes(manufacturer, fill = manufacturer)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_rpg(palette = "rpg_rainbow_no_grey", guide = "none")
```

## Geographic Data with ggplot2

These palettes can also be used with ggplot2 to display geographic data with both continuous and discrete scales, uses the scale fill function.

### Discrete Palettes
```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "logo")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "additional")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "main and additional")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "rpg_colors")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "rpg_cold_warm")
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = province)) +
  scale_fill_rpg(palette = "rpg_rainbow")
```

### Continous Palettes
```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "logo", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "additional", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "main and additional", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "shale_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "green_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "red_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "earth_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "teal_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_orange_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "gray_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "sea_green_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_blue_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "navy_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "black_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "chartreuse_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "gold_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "burnt_orange_ramp", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_colors", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_cold_warm", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_rainbow", discrete = FALSE)
```

```{r}
ggplot(NLD_muni) +
  geom_sf(aes(fill = population)) +
  scale_fill_rpg(palette = "rpg_rainbow_no_grey", discrete = FALSE)
```

## Geographic Data with tmap

tmap uses a differing syntax from ggplot however by using the rpg_color_pal function, with a step count indicated, and saving the output to an object these palettes can be used in tmap.

### Discrete Palettes
```{r}
MyPal <- rpg_color_pal("logo")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("main and additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_colors")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_cold_warm")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_rainbow")(10)
tm_shape(NLD_muni) +
  tm_polygons("province", palette = MyPal) 
```

### Continous Palettes
```{r}
MyPal <- rpg_color_pal("logo")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("main and additional")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("shale_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("green_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("red_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("earth_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("teal_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_orange_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("gray_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("sea_green_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_blue_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("navy_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("black_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("chartreuse_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("gold_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("burnt_orange_ramp")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_colors")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_cold_warm")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal) 
```

```{r}
MyPal <- rpg_color_pal("rpg_rainbow")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```

```{r}
MyPal <- rpg_color_pal("rpg_rainbow_no_grey")(10)
tm_shape(NLD_muni) +
  tm_polygons("population", palette = MyPal)
```
