---
title: "rpgcolorsr User Guide"
author: "Brian Froeb"
date: "6/29/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r echo=FALSE}
library(ggplot2)
library(tmap)
library(rpgcolorsr)
data(NLD_muni)
```

There are currently 71 colors included in this package the color names and their hex codes are below
```{r, echo=FALSE}
rpg_color_list
```

These are grouped into 20 color palettes, the colors included in each palette and their hex codes are below
```{r, echo=FALSE}
rpg_color_palettes
```

These color palettes can be inserted into ggplot graphics, examples of each palettes in ggplot are below

## Functions Included

This package includes four functions:

-rpg_cols()
-rpg_color_pal()
-scale_color_rpg()
-scale_fill_rpg()

#### rpg_cols
takes a input string or group of strings and returns the hex code. 
The color must be one of the colors included in this package

##### Example:
```{r}
rpg_cols("blue")

rpg_cols("teal", "black")
```

#### rpg_color_pal

Converts an input string representing a color palette into a function that can be converted into a usable color palette.

```{r}
rpg_color_pal("rpg_cold_warm")
```

By adding a step count after the function it will return a usable palette

```{r}
rpg_color_pal("rpg_cold_warm")(10)
```

These palettes can be reversed as needed

```{r}
rpg_color_pal("rpg_cold_warm", reverse = TRUE)(10)
```

#### scale_color_rpg and scale_fill_rpg

These functions supply a fill or color to a ggplot call. See examples below.

